Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-10-26 journal/ms.tex
journal

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure can be characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words (Collins and Loftus, 1975). Previous studies have
investigated early vocabulary structure by constructing networks using a
variety of word-word relations including shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological similarity. These studies have
found that children tend to produce words that have higher neighborhood
density (i.e., high connectivity in the network) earlier, both at the
phonological and the semantic level (Engelthaler \& Hills, 2017; Hills,
Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009) add
Beckage, 2011 and other people\ldots{}

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will rename these scenarios in a
ways that reflects how their modes of operation contrast with each
other. We will call preferential attachment the Internally-driven
mechanism (INT), and preferential acquisition the Externally-driven
mechanism (EXT). Figure~\ref{fig:growth} shows an illustration of both
growth scenarios with the same simplified network. These two proposals
represent two divergent ideas about the role of lexical networks in
acquisition. On the INT proposal, network structure is a causal factor
in early word learning; in contrast, on the EXT approach, network
structure is not internally represented and, therefore, might be an
epiphenomenon of the statistics of the linguistic input.

@@

Hills et al. (2009) found that early networks do not grow through INT as
was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
through EXT. This finding, though potentially very profound, has only
been estabished in the special case of networks that are 1) based on
semantic associations, 2) use data from English-learning children, and
3) consider word production as a measure of acqusition. Thus, it could
be that the result depends on the domain, culture or/and the measure. In
this work, we test the generality of the finding along these three
dimesnions.

First, we investigte the mechanism that underlies the growth of
phonological networks. Previous studies have analyzed various strcutural
properties of adults phonological networks, and found that some of these
properties influence the language processes of word recognition and
production as well as language-related memory processes (Vitevitch,
2008; Luce \& Pisoni, 1998; Chan \& Vitevitch, 2009; Chan \&
Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al.
2018). More relvant to our study is the research that investigates
learning in children, and in particualr the finding that words'
connectivity in a phonological network is negatively correlated with
their age of learning in children (Stokes 2004; Storkel, 2004, 2009). In
other words, the finding suggests that words learned earlier tend to
sound similar to many other words than a word learned later in life.
This finding however, does not address the question of the learning
mechanism. In fact, as with semantic networks, the fact that the
connectivity in the end-state network predicts AoA can be the outcome of
both the internallay- and externally-driven mechanisms (Hills et al.
2009).

Second, we test how the proposed growth mechanims predict word
comprehension as compared to production. These two measures differ in
their assessment of vocabulary composition (e.g., Benedict, 1979).
Testing both measures is critical as it allows us to investigate the
extent to which the mechanism is infleunced by production constraints
(i.e., how difficult a word is to say) as compared to comprehension
constraints (i.e., how difficult it is to store or access). If there is
consistency across both measures, this would suggest that the growth
mechanism captures learning patterns beyond these specific constraints.

Finally, we use developmental data of children in 10 cultures. Such
cross-linguistic comparison is crucial to test what growth mechanism is
cognitively universal and is used by all children, and what mechansism
is specific to some patterns of learning that emerge due to the
particulars of a given language or culture (Bates \& MacWhinney, 1987;
Slobin, 1985). More precisely, we test whether Hill's finding with
English-learning data generalize to other languages, and we test whether
this generalization holds for both the semantic and phonological
networks, and for both the comprehension and production data.

we test the growth mechanim in the phonological domain. Although
previous results showed that \ldots{} (Storkel,), the growth mechanim
has never been tested. The outcome could enrich the debate as to whether
children first learn the words that (Here I should read the Dautrich
paper). Second, we use developmental data collected from children in 10
cultures. Third, we compare results using production and comprehension
as measures of acuquition.

Why phonological domain is important Why languages are important Why
comprehension is important

whether phonological networks, like semantic networks, grow by , or if
they rather grow by P

Studies that investigate lexical network growth have focused on semantic
networks using the English vocabulary and development data based on word
production. In particualr,

However, the lexicon is not only strctured semantically

Our work expands this previous research in three ways: 1) we test
whether

The novelty of the current study is threefold: First, it investigates
whether phonological networks, like semantic networks, grow by PAC, or
if they rather grow by PAT. Second, it provides a systematic comparison
of both network growth scenarios in the phonological and the semantic
domains and assesses their relative contribution to the learning
process. Third, it tests the generality of the findings across eight
languages.

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). We used the
\emph{Words and Sentences} version of the CDI which contains the
productive vocabulary of toddlers (age varied between 16 to 36 months).
Following previous studies (Hills et al., 2009; Storkel, 2009), we
restricted our analysis to nouns. We defined the age of acquisition of a
given word by the month at which this word was produced by at least 50\%
of children (J. C. Goodman et al., 2008), and we excluded nouns that
have not been learned (according to this criterion) by the last month
for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English,
Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
nouns that had entries in the Florida Association Norms (see below).
Since these norms are available only in English, we used the
hand-checked translation equivalents provided by Braginsky et al.
(2016), allowing us to use the English association norms across
languages. Table \ref{tab:stats} gives an overview of the data used.
Translation equivalents were originally constructed for a subset of
words appearing on the toddler CDI form, and so not all words are
currently available. Note, however, that all languages have at least
60\% of nouns translated.

@@

\section{Semantic networks}\label{semantic-networks}

We constructed semantic networks following the procedure outlined in
Hills et al. (2009). We used as an index of semantic relatedness the
Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
This dataset was collected by giving adult participants a word (the
cue), and asking them to write the first word that comes to mind (the
target). For example, when given the word \enquote{ball}, they might
answer with the word \enquote{game}. A pair of nodes were connected by a
directed link from the cue to the target if there was a cue-target
relationship between these nodes in the association norms. The
connectivity of a given node was characterized by its \emph{indegree}:
the number of links for which the word was the target. To model growth
from month to month, we constructed a different network at each month,
based on the words that have been acquired by that month.

@@

We generated approximate International Phonetic Alphabet (IPA)
transcriptions from the orthographic transcription, across languages,
using the open source text-to-speech software
\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
the Levenshtein distance (also known as edit distance) as a measure of
phonological relatedness between two nodes. The measure counts the
minimum number of operations (insertions, deletions, substitutions)
required to change one string into another.

@@

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds to the network
by 30 months). This global network is the end-state towards which both
PAT and PAC should converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that are relevant to PAC
and/or PAT.

@@

Connectivity in the global network is directly related to PAC as it
represents the explicit criterion PAC uses to determine what words
should be learned first (Figure \ref{fig:growth}). Therefore, a direct
consequence of a PAC-like growth scenario is a correlation between
connectivity in the global network and the age of
acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
Figure \ref{fig:corrAll} shows how the age of production (A) and
comprehension (B) for each word varies as a function of its degree (or
indegree for the semantic network). For ease of visual comparison, the
predictor (i.e., the degree) was centered and scaled across languages.
The plots show, overall, a negative correlation between the month of
acquisition and the degree, indicating that nouns with higher degrees
are generally learned earlier.

@@

\subsubsection{Power-law degree
distribution?}\label{power-law-degree-distribution}

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to PAT as this growth
scenario is known to generate networks with a power-law degree
distribution (i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
network displays this property, this fact would suggest a PAT-like
generative process. Conversely, if the degree distribution does not
follow a power law, this fact would weaken the case for PAT. The log-log
plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
each empirical degree distribution following the procedure outlined in
Clauset, Shalizi, and Newman (2009) and using the related R package
(poweRlaw, Gillespie, 2015). In brief, the analysis consisted in two
steps. First, we derived the optimal cut-off, \(k_{min}\), above which
the distribution is more likely to follow a power
law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
and we estimate the corresponding scaling parameter \(\alpha\). Second
we calculated the goodness-to-fit, which resulted in a \(p\)-value
quantifying the plausibility of the model. The results are shown in
Appendix 1, table XX. Overall, we could not reject the null hypothesis
of a power-law distribution: the \(p\)-value was generally above 0.1.

In sum, the static properties of the global network are \emph{a priori}
compatible with both PAT and PAC. In order to decide between these two
developmental scenarios, we need to fit explicit growth models to the
data.

@@

We saw that the way semantic and phonological information is structured
in the learning environment (i.e., PAC) contributes to noun learning
across languages. However, we know that other factors influence learning
as well (e.g., Braginsky et al., 2016). Next we investigated how
semantic and phonological connectivity interact with two other factors.
The first one is word frequency, a well studied factor shown to predict
the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
2008). The second factor is word length, which correlates with
phonological connectivity.

Since PAT was uninformative, we dropped it from this analysis, keeping
only PAC. This simplified the model because we no longer needed to fit
growth
month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
A more direct way to assess and compare the contribution of PAC in
relation to other word-level factors is through conducting linear
regressions, where connectivity in the learning environment, frequency
and length predict the age of acquisition.

We used the frequency estimates from Braginsky et al. (2016) where
unigram counts were derived based on CHILDES corpora in each
language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
For each word, counts included words that shared the same stem (e.g.,
\enquote{cats} counts as \enquote{cat}), or words that were synonymous
(e.g. \enquote{father} counts as \enquote{daddy}). For word length, we
counted the number of phonemes in our generated IPA transcription.

We conducted two analyses. We fit a linear regression for each language,
and we fit a linear mixed-effect model to all the data pooled across
languages, with language as a random effect. Figure \ref{fig:staticPred}
shows the coefficient estimate for each predictor in each language for
production and comprehension data. Figure \ref{fig:staticAll} shows the
coefficient estimates for all languages combined (all predictors were
centered and scaled). The findings were as follows. Overall, frequency
is the largest and most consistent predictor of age of acquisition,
replicating results for nouns across a variety of analyses (Braginsky et
al., 2016; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
length predicts learning in some languages such as Croatian and
Norwegian, but not in others (including English). It remains, however, a
significant predictor in the global model. As for the factors of
interest, i.e., semantic and phonological connectivity, we also found
cross-linguistic differences. Phonological connectivity contributes to
learning in languages such as Croatian, English and Russian, whereas
semantic connectivity contributes to learning in Turkish, Spanish and to
some extent in Croatian, but not in
English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in Hills et al. 2009. However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates. Another important difference is the number of words tested: Our study uses a larger set of nouns.}
Despite these cross-linguistic differences, both phonological and
semantic connectivity are significant predictors in the combined model.

@@

The present study provided a comprehensive analysis of how lexical
connectivity influences the age of acquisition of nouns in toddlers. We
compared two network growth scenarios and assessed their relative
contributions across eight languages. One scenario, PAT, described a
rich-get-richer network growth model in which the structure of the
learner's internal network determines future growth; the other, PAC,
described a model in which the external, global environmental network
structure determines learners' growth patterns. Our findings largely
replicate the results obtained by Hills et al. (2009): Semantic networks
grow by preferential acquisition, not by preferential attachment. A
novel finding is that phonological networks also grow primarily by
preferential acquisition. Moreover, both semantic and phonological
connectivity in the learning environment predict growth. These findings
generalize well across languages. When pitted against other known
predictors of age of acquisition (word frequency and length), the effect
of word connectivity shows a cross-linguistic variation, predicting
learning in some languages, but not in others. Nevertheless, this
cross-linguistic variability is to be taken with a grain of salt as it
might be exaggerated in our study by the limited and
partially-overlapping sample of nouns for each language. In fact, both
phonological and semantic connectivity are significant predictors when
data are pooled across languages.

Children start by learning words that have high semantic and
phonological similarity to a variety of other words in the learning
environment, not in the child's available lexicon. This result suggests
that children are sensitive to connectivity even without having first
acquired the connected words. How can children indirectly detect highly
connected words, and why would such words be more readily learned?

In the semantic case, the networks are based on free association norms.
These associations can be (partly) derived from the patterns of
word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
i.e., two words are associated if they co-occur in many different
contexts. In a network structure, highly connected words would be the
words that co-occur with many other words in various contexts. Why would
such words be easier to learn? One possibility, suggested by Hills et
al. (2010), is that the referents of these words are more easily
disambiguated from other potential referents because their presence in
multiple contexts provides more cross-situational, disambiguating
statistics about their true referents (Smith \& Yu, 2008).

In the phonological case, connectivity is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Even infants show a sensitivity for high frequency sound sequences in
the ambient language (Jusczyk, Luce, \& Charles-Luce, 1994). Moreover,
phonotactic probability facilitates learning and recognition (e.g.,
Storkel, 2001). In other words, children's sensitivity to local
phonotactic regularities might lead them to learn higher-probability
words more easily. This learning effect, in turn, would lead to an
observed pattern of growth that would appear to follow the PAC growth
model even though learners themselves would only be tracking local
statistics.

Finally, while validating previous results using network growth models,
our study suggests that these correlational patterns may emerge from the
operation of simpler mechanisms in both the semantic and phonological
domains. One question for future experimental work is whether such
patterns of growth can be produced in controlled behavioral experiments.

@@

@@

\hypertarget{ref-griffiths07}{}
Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
semantic representation. \emph{Psychological Review}, \emph{114}(2),
2007.

>>>>

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure can be characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words (e.g., Collins and Loftus, 1975). Previous studies have
investigated early vocabulary structure by constructing networks using a
variety of word-word relations including shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological similarity. These studies have
found that children tend to produce words that have higher neighborhood
density (i.e., high connectivity in the network) earlier, both at the
phonological and the semantic level (Engelthaler \& Hills, 2017; Hills,
Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \&
Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009) add
Beckage, 2011 and other people\ldots{}

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will call preferential
attachment the Internally-driven mechanism (INT), and preferential
acquisition the Externally-driven mechanism (EXT).
Figure~\ref{fig:growth} shows an illustration of both growth scenarios
with the same simplified network. These two proposals represent two
divergent ideas about the role of lexical networks in acquisition. On
the INT proposal, network structure is a causal factor in early word
learning; in contrast, on the EXT approach, network structure is not
internally represented and, therefore, might be an epiphenomenon of the
statistics of the linguistic input.

@@

Hills et al. (2009) found that early lexical networks do not grow
through INT as was originally hypothesised by Steyvers and Tenenbaum
(2005), but rather through EXT. This finding, though potentially very
profound, has only been estabished in the special case of networks that
are based on 1) semantic associations, 2) word production as a measure
of acquisition, and 2) data from English-learning children, only. The
extent to which this result depends on the domain, the measure and
culture/languagae is still unclear. In this work, we test the generality
of the finding along these three dimesnions.

First, we study the phonological network in addition to the semantic
network. These two networks represent different ways the mental lexicon
is strcutured. In particular, words that are neighbors in the semantic
network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
neighbors in the phonological network, and vice versa. Does the
phonological network also influence word learning? Previous work did
find an effect of words' connectivity in the phonological network on
their age of learning (Storkel, 2004, 2009; Stokes 2014). In other
words, words learned earlier in life tend to sound similar to many other
words than a word learned later in life. However, as mentioned above,
this finding did not examine the underlying learning
mechanism.\footnote{In particular, this finding is compatible with both INT and EXT.}
Here, we investigate whether phonological networks, like semantic
networks, grow through EXT, or if they rather grow via INT
(Figure~\ref{fig:growth}).

Second, we study vocabularies measured using both comprehension and
production. Previous studies have found differences between these
vocabularies in terms of their content and rate of acquistion (Benedict,
1979; Fensen et al. 1993). These differences can be due to the fact that
comprehension and production do not share the same contraints. For
instance, whereas comprehension depends on the ease with which words are
stored and accessed, production depends additionally on the ease with
witch words are articuated (e.g., shorter words are produced earlier,
Braginsky et al. 2016). By including comprehension-based vocabularies in
our analysis, we assess the extent to which the network growth
mechanisms capture general learning patterns beyond the specific
constraints of production.

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-lingustic variability along both the semantic
and phonological domains (Youn et al. 2015; Arbesman et al.
2009).\footnote{The difference is more obvious in the phonolgical case where the network strcuture––and the distribution of word connectivity––can a priori change from language to language depending on various languisitc conventions.}
Besides, cultures might differ in the way caregivers guide the
chidlren's learning patterns or in the way the adults' linguistic input
is organized (Kuhl et al., 1997; Cristia et al. 2017), and this
difference could influecne the learning mechanism. Thus,
Cross-linguistic comparison is crucial to test what mechanism is
cognitively universal and is used by all children, and what mechansism
is specific to some patterns of learning that emerge due to the
particulars of a given language or culture (Bates \& MacWhinney, 1987;
Slobin, 1985).

HERE ORGANIZATION OF THE PAPER

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). When filling
out a CDI form, caregivers are either invited to indicate whether their
child \enquote{understands} (comprehension) or \enquote{understands and
says} (production) for each of about 400 words. For youner chidlren
(between 8 and 18 months), both comprehension and production are
queried, whereas for oder chidlren (between 16 to 36 months) only
production is queried. We use data from younger chidlren to test
comprehension and data from older chidlren to test production. Following
previous studies (Hills et al., 2009; Storkel, 2009), we restrict our
analysis to nouns. Table \ref{tab:stats} gives an overview of the data
source.

\subsection{Age of acquisition}\label{age-of-acquisition}

For each word in CDI data, we compute the proportion of children who
understand or produce the word at each month. Then we fit a logistic
curve to these proportions and determined when the curve crosses 0.5,
i.e., the age at which at lest 50\% of chidlren know the word. We take
this point in time to be each word's age of acquisition (J. C. Goodman
et al., 2008) and Braginsky.

@@

\subsection{Semantic networks}\label{semantic-networks}

We constructed semantic networks for English data following the
procedure outlined in Hills et al. (2009). We used as an index of
semantic relatedness the Florida Free Association Norms (Nelson, McEvoy,
\& Schreiber, 1998). This dataset was collected by giving adult
participants a word (the cue), and asking them to write the first word
that comes to mind (the target). For example, when given the word
\enquote{ball}, they might answer with the word \enquote{game}. A pair
of nodes were connected by a directed link from the cue to the target if
there was a cue-target relationship between these nodes in the
association norms. The connectivity of a given node was characterized by
its \emph{indegree}: the number of links for which the word was the
target. To model growth from month to month, we constructed a different
network at each month, based on the words that have been acquired by
that month.

Free Association norms are available only in English. We used the
hand-checked translation equivalents available in Wordbank, which
allowed us to use the English association norms across languages. Note
that this does not necessarily mean that the resulting networks will be
the same across languages, or that these networks will grow similarly.
Though using the same association data acoss langauges assumes that the
semantic similarity measure is universal (which is a reasonable
approximation, Youn et al. 2015), the set of words acquired by children
as well as the timeline of this acquisition can still vary from language
to language leading to possbility different learing strategies.

@@

To construct phonological networks we first mapped the orthogrphic
transcrition of words to their International Phonetic Alphabet (IPA)
transcriptions, across languages, using the open source text-to-speech
software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.}
We used the Levenshtein distance (also known as edit distance) as a
measure of phonological relatedness between two nodes. The measure
counts the minimum number of operations (insertions, deletions,
substitutions) required to change one string into another.

@@

We start by analyzing word connectivity in the global (static) network.
We constructed this network using nouns learned by the oldest age for
which we have CDI data (e.g., in English this corresponds, in
comprehension, to the network by 18 months, and in production, to the
network by 30 months). This global network is the end-state towards
which both INT and EXT converge by the last month of learning. Moreover,
following Hills et al. (2009), we used this end-state network as a proxy
for the external connectivity in the learning environment. Below we
analyze properties of this global networks that are relevant to INT
and/or EXT.

@@

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of a EXT-like growth scenario is a correlation
between connectivity in the global network and the age of
acquisition.\footnote{This correlation is also compatible with INT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
Figure \ref{fig:corrAll} shows how the age of production (A) and
comprehension (B) for each word varies as a function of its degree (or
indegree for the semantic networks). For ease of visual comparison, the
predictor (i.e., the degree) was centered and scaled across languages.
The plots show, overall, a negative correlation between the month of
acquisition and the degree, indicating that nouns with higher degrees
are generally learned earlier. HERE MENTION THE AVERAGE VALUE OF THE
CORRELATIONS

@@

\subsubsection{Power-law degree
distribution}\label{power-law-degree-distribution}

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to INT as this growth
scenario is known to generate networks with a power-law degree
distribution (i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
network displays this property, this fact would suggest a INT-like
generative process. Conversely, if the degree distribution does not
follow a power law, this fact would weaken the case for INT. The log-log
plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
each empirical degree distribution following the procedure outlined in
Clauset, Shalizi, and Newman (2009) and using the related R package
(poweRlaw, Gillespie, 2015).

In brief, the analysis consisted in two steps. First, we derived the
optimal cut-off, \(k_{min}\), above which the distribution is more
likely to follow a power
law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
and we estimate the corresponding scaling parameter \(\alpha\). Second
we calculated the goodness-to-fit, which resulted in a \(p\)-value
quantifying the plausibility of the model.

The results are shown in table XX. Overall, we could not reject the null
hypothesis of a power-law distribution: the \(p\)-value was generally
above 0.1. Also talk about the fact that the power law is truncated.

In sum, the static properties of the global network are \emph{a priori}
compatible with both INT and EXT. In order to decide between these two
developmental scenarios, we need to fit explicit growth models to the
data.

@@

We saw that the way semantic and phonological information is structured
in the learning environment (i.e., EXT) contributes to noun learning
across languages. However, we know that other factors influence learning
as well (e.g., Braginsky et al., 2016). Next we investigated how
semantic and phonological connectivity interact with two other factors.
The first one is word frequency, a well studied factor shown to predict
the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
2008). The second factor is word length, which correlates with
phonological connectivity: Shorter words are more likely to have higher
connectivity (Pisoni et al., 1985; Vitevitch and Rodriguez, 2004), and
thus it critical to test if phonological connectivity plays a role in
learning above and beyond word length.

Since the previous section showed that INT was uninformative, we dropped
it from this analysis, keeping only EXT. This simplified the model
because we no longer needed to fit growth month-by-month.The latter was
a requirement only for INT where the words' utilities varied from month
to month, depending on how connectivity changed in the growing internal
network. A more direct way to assess and compare the contribution of EXT
in relation to other word-level factors is through conducting linear
regressions, where connectivity in the learning environment, frequency
and length predict the age of acquisition.

For word length, we counted the number of phonemes in our generated IPA
transcription. For word frequency, we used the frequency estimates from
Braginsky et al. (2016) where unigram counts were derived based on
CHILDES corpora in each language (MacWhinney, 2000). For each word,
counts included words that shared the same stem (e.g., \enquote{cats}
counts as \enquote{cat}), or words that were synonymous (e.g.
\enquote{father} counts as \enquote{daddy}). Note that these frequency
counts are based on transcripts from independent sets of children and
represent a general estimate of environmental frequency across children.
The use of an independent dataset is warraned because it uses large
samples to average out the difference between children (see Goodman et
al. 2008).

We conducted two analyses. We fit a linear regression for each language,
and we fit a linear mixed-effect model to all the data pooled across
languages, with language as a random effect. Figure \ref{fig:staticPred}
shows the coefficient estimate for each predictor in each language for
production and comprehension data. Figure \ref{fig:staticAll} shows the
coefficient estimates for all languages combined (all predictors were
centered and scaled).

The findings for the new predictors were as follows. Overall, frequency
is the largest and most consistent predictor of age of acquisition in
both comprehension and production data and across languages, endorsing
results for nouns across a variety of analyses (Braginsky et al., 2016;
J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
predictive for production than comprehension (and this difference is
very clear in the global model), replicating previous work (Braginsky et
al., under review). Thus, word length seems to reflect the effects of
production constraints rather than than comprehension constraints (i.e.,
long words are harder to pronounce than short words, but maybe not more
difficult to store or access).

As for the factors of interest, i.e., semantic and phonological
connectivity, we found cross-linguistic differences. Phonological
connectivity contributes to learning in some languages but not in other.
In particular, semantic connectivity does not explain variance in
English data beyond that explained by phonological connectivity,
frequency and length. This contrasts with the original finding in Hills
et al. (2009). However, in this previous study, semantic connectivity
was not tested in a model that included frequency, length and
phonological connectivity as covariates. Another important difference is
the number of words tested: Our study uses a larger set of nouns. That
said, and despite these cross-linguistic differences, both phonological
and semantic connectivity are significant predictors in the combined
model.

@@

This study provided an analysis of network growth during development. We
compared the two major network growth scenarios desribed in the
pioneering work of Hills et al. (2009). The first scenario, INT
(orignially called Preferentailly Attachement), described a
rich-get-richer network growth model in which the current structure of
the learner's internal network determines future growth; the other, EXT
(orignially called Preferentailly Acquisition) described a model in
which the external, global environmental network structure determines
learners' growth patterns. Previous word in this line of research (e.g.,
Hills et al. (2009); Hills et al. (2010); Sailor 2013) has been limited
in its scope: It focused on semantic networks, while relying only on
words' production as a mesure of their acquisition, and using almost
exclusively developmental data from English-learning children. This
study test the generality previous findings first by investigting
phonological networks together with semantic networks, second by
adopting both production and comprehension as measures of learing, and
crucially, by comparing the findings across 10 languages.

We found that the orginal findings reported in Hills et al. (2009)
generalize well across all these dimensions. First, just like semantic
networks, phonological networks grow via the externally-driven scenrio
(EXT), not by the internally-driven mechanism (INT). Besides, both
semantic and phonological networks contribute to the learning process
above and beyond other known predcitors of word learning such as
frequency and word length. Second, comprehension-based vocabularies grow
in a way similar to production-based vocabularies {[}HERE ADD MORE
NUANCE?{]}. Finally, the findings were overall similar across the 10
languages we tested. Although we find some cross-lingusitic variation
when semantic and phonological networks were pitted against frequency
and length, this variability is to be taken with a grain of salt as it
might be exaggerated in our study by the limited and
partially-overlapping sample of nouns for each language. In fact, both
phonological and semantic connectivity are significant predictors when
data are pooled across languages.

These findings corroborate the hypothesis that children start by
learning words that have high similarity to a variety of other words in
the learning environment, not in the child's available lexicon. This
means, strikingly, that children are sensitive to highly connected words
although they do not initially have access to the full network. This
remarks begs the following question: What mechanism could allow children
to tease apart highly connected words from low connected words? Besides,
why would highly connected words be easier to learn?

One possbility is that children rely on their statistical learning
abilities. For example, in the semantic domain, children might be using
a mechanism akin to cross-situational learning to pick up the meanings
of some words, especially concrete nouns (Smith \& Yu, 2008), and such
learning would resemble the growth scenario described by EXT. Indeed,
since free association is related to contextual co-occurrence (Griffiths
et al., Fourtassi and Dupoux, 2013), highly connected words will tend to
occur in a variety of speech and referential contexts. This fact makes
such a word easier to learn only because it has more referential
disambiguating cues across learning contexts, and crucially, even
without knowing the entire set of words with witch it occurs (hence the
similarity with EXT). This possibility is supported by the finding that
nouns' diverstiy of occurrence in child directed speech predicts their
age of learing (Hills et al. (2010)).

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking lwo level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
\& Charles-Luce, 1994) and this sensitivity might lead them to learn
higher-probability words more easily (e.g., Storkel, 2001). This
explanation is supported by computational simualtions that shows how
learning general phonotactics patterns create ``well-worn paths'' which
allow for the representation of several distinct but phonologically
neighboring words (Dell et al; 1993; Tavac et al. 2017).

Besides using their own statitistical learning skills, children could
also benefit from the the way their caregivers speak. Perhaps the
cargivers put more emphasis on the words that are highly connected in
\emph{their} mature lexical network. This emphasis would guide children
to learn first these highly connected words even though children do not
have access to the distribution of words' connectivity in the final
network. Investigting this possibility would require further research on
caregiver-child interaction (MacWhinney, 2014; Roy et al. 2015),
examining what words are introduced over development and the extent to
which children's uptake is infuence by this input (Clark 2007; Hoff and
Naigles, 2002; Hurtado et al., 2008).

This work shares a number of limitations with previous studies using
similar research strategy and datasets (e.g., Hills et al. 2009; 2010).
Chief among these limitations is the fact that the age of word
acquisition is computed using different children at different ages (due
to the fact that avialable CDI data is mainly cross-sectional). Althoug
this measure has proven highly consistent (Fensen et al. 1993), it lead
us to focus on studying the learning mechanism of the \enquote{average}
child. Individual trajectories, however, could show different learning
patterns. For example, using longitudinal data Beckage, Smith, and Hills
(2011) found differences between typical and late talkers in terms of
the semantic network structure. Besides, although our study endorses the
externally-driven account of network growth, this does not mean
individual children never use some variant of the internally-driven
mechanism. For instance, some children develop \enquote{islands of
expertise}, that is, well organized knowledge about a certain topic
(e.g., birds or dinosaurs). This prior knowledge enables these children
to learn new related words more easily (e.g., Chi and Koeske, 1983).

To conclude, our work validates previous results in early network
development, and suggests that the advantage of highly connected words
words may emerge, at least in the early stages of word learning, from
the operation of simpler mechanisms in both the semantic and
phonological domains. One question for future experimental work is
whether such correlational patterns of growth can be produced in
controlled behavioral experiments.

@@

\hypertarget{ref-beckage2011}{}
Beckage, N. M., Smith, L., \& Hills, T. T. (2011). Small worlds and
semantic network growth in typical and late talkers. \emph{PLOS ONE},
\emph{6}(5), 1--6.

@@
